---
title: "PCA and K Means"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(cluster)
library(factoextra)
```

## Instruction

Dataset: Iris
Task: 

Doing the PCA so that it reduces Iris data to only 2 columns.
Then, doing K-Means Clustering from the successful Iris data
reduced. After that, answering the 3 questions below:

Question:
a. What are values of the eigenvalue 1 and eigenvalue 2 of the Iris dataset?
b. How much information can still be 'explained' by the reduced data?
c. Find the optimal 'k' value based on the Elbow and Silhouette method.Is the value of k = 3 still the best 'k' value?

```{r}
# Import data iris
data(iris)

# Create new data frame without feature target
df <- cbind(iris$Sepal.Length, iris$Sepal.Width, iris$Petal.Length, iris$Petal.Width)
```

```{r}
# Create PCA
pca_iris = prcomp(df, center = TRUE, scale = TRUE)
```

```{r}
# Checking the summary of PCA model for decided the eigenvalue 1 and 2
summary(pca_iris)
```

```{r}
# To find the eigenvalues of the PCA, we can square the 'standard deviation'
pca_iris$sdev^2
```

```{r}
# Reduce the iris data to only 2 columns
iris_transform = as.data.frame(-pca_iris$x[,1:2])
iris_transform
```

```{r}
# Do a k-means evaluation of iris_transform
fviz_nbclust(iris_transform, kmeans, method = 'wss')
fviz_nbclust(iris_transform, kmeans, method = 'silhouette')
```

```{r}
# Choose the number K that you think is the most optimal
k = 2
  
# Visualize K-Means clustering on the reduced Iris data
kmeans_iris = kmeans(iris_transform, centers = k, nstart = 50)
fviz_cluster(kmeans_iris, data = iris_transform)
```

Answers:
a. Eigenvalue 1: 2.91849782 Eigenvalue 2: 0.91403047
b. If we only choose PC1, we are still able to explain 72.9% of the data spread. If we choose PC1 and PC2, we are still able to explain 95.8% of the data spread
c. The optimal K value = 2, the best K value is 2 because if we choose 3, it is no longer in the elbow and a normal decrease is seen (increasing the number of clusters is no longer significant in reducing WSS) after k = 2 and if we compare the results k = 2 with k = 3, the results tend to be close to or similar to k = 3 for k = 2, so it is better to combine them into k = 2 because there is no significant difference
